Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex
bench section: add a sentence about the equal strings

\begin{code}
Smalltalk garbageCollect.
#(0 1 5 100 1000) collect: [ :size |
	| iterations time overhead |
	collection := ByteString new: size.
	collection2 := ByteString new: size.
	size < 100 ifTrue: [iterations := (100000000 // (size*10 max: 1) sqrt) floor.]
			   ifFalse: [iterations := (10000000 // size sqrt) floor.].
	overhead := [ 1 to: iterations do: [ :i | ] ] timeToRun.
	time := [ 1 to: iterations do: [ :i |
		collection compareWithSlang: collection2 ] ] timeToRun.
	stream nextPutAll: ((time - overhead) asString)].
\end{code}\\

@@

\cba{+ we bench only = strings, which could make a difference on the plugin version (one less branch) - maybe we should change to number of character compared instead of string size so it does not imply the string are equals.}

@@

\begin{figure*}[bth]
		\centering
		\includegraphics[width=1\linewidth]{figures/asm_cmp.pdf}
		\caption{GCC and LLVM: different optimizations on the comparison loop \cba{on peut enlever les adresses je pense ca sert a rien en vrai et comme ca les fonts pourront etre plus grosses}}
		\label{fig:Asm}
\end{figure*}

>>>>

\begin{code}
#(0 1 5 100 1000) collect: [ :size |
	| iterations time overhead |
	collection := ByteString new: size.
	collection2 := ByteString new: size.
	size < 100 ifTrue: [iterations := (100000000 // (size*10 max: 1) sqrt) floor.]
			   ifFalse: [iterations := (10000000 // size sqrt) floor.].
	overhead := [ 1 to: iterations do: [ :i | ] ] timeToRun.
	time := [ 1 to: iterations do: [ :i |
		collection compareWithSlang: collection2 ] ] timeToRun.
	stream nextPutAll: ((time - overhead) asString)].
\end{code}\\

@@

The 2 compared strings are equal as it corresponds to the worst scenario for most of our benched implementations \footnote{There is one branch less in the SlangPlugin implementation in this case}.

@@

\begin{figure*}[bth]
		\centering
		\includegraphics[width=1\linewidth]{figures/asm_cmp.pdf}
		\caption{GCC and LLVM: different optimizations on the comparison loop}
		\label{fig:Asm}
\end{figure*}
